### 2023-06-08 README.Rmd
update v01 230608

---
output: github_document
---

@@

The goal of validateHOT is to validate the results of your validation task (also known as holdout task). A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores. At the moment, validateHOT provides the following functions:

@@

This is a basic example which shows you how to solve a common problem:

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

>>>>

---
output: github_document
bibliography: references.bib
---

@@

The goal of validateHOT is to validate the results of your validation task (also known as holdout task). A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores. At the moment, <code>validateHOT</code>
provides functions for 3 key areas:

<ul>
<li>validation metrics mainly reported in preference measurement
studies</li>

<li>metrics that are usually reported in machine learning (i.e.,
confusion matrix)</li>

<li>simulation methods, for example, to determine optimal product
combinations</li>

</ul>

For all 3 key areas, the <code>createHOT</code> function is essential.
This function creates the total utilities for each alternative in the
validation/holdout task and also in the simulation method, respectively.
@rao2014a [p. 82] mentions the additive utility model stating that the
total utility of a profile or conjoint model is the sum of its attribute
levels. <code>createHOT</code> will do exactly this for you.

### Classical validation metrics

<ul> <li><code>hitrate</code>: </li>

<li><code>mhp</code>: </li>

<li><code>kl</code>: </li>

<li><code>mae</code>: </li>

<li><code>medae</code>: </li>

<li><code>mhp</code>: </li>

<li><code>rmse</code>: </li>

</ul>

### Confusion Matrix

<ul>

<li><code>accuracy</code>: </li>

<li><code>f1</code>: </li>

<li><code>precision</code>: </li>

<li><code>recall</code>: </li>

<li><code>specificity</code>: </li>

</ul>

### Simulation Methods

<ul>

<li><code>freqassort</code>: </li>

<li><code>reach</code>: </li>

<li><code>shareofpref</code>: </li>

</ul>

### Data Frames provided by <code>validateHOT</code>

<ul>

<li><code>ACBC_interpolate</code>: </li>

<li><code>ACBC</code>: </li>

<li><code>CBC_lin</code>: </li>

<li><code>CBC</code>: </li>

<li><code>MaxDiff</code>: </li>

</ul>

@@

## References
